---
title: "Sticky Attributes"
author: "Christopher Brown"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Sticky attributes are additional functionality that make attributes resilent 
various manipulations operations including:

- subset
- extend
- append
- insertion into a list-like object such as a data.frame or data.table
- slices from a data.frame or data.table

Basically, the attributes stick with the object much like attributes do in other
languages.


## Limitations

There are a few areas where the methods of this package breakdown:


## References

The issue of attribute resilence has been often asked and debated. Here are a 
few of the most prevalent discussions.

- [loss-of-attributes-despite-attempts-to-preserve-them](http://stackoverflow.com/questions/23991060/loss-of-attributes-despite-attempts-to-preserve-them)
- [how-to-delete-a-row-from-a-data-frame-without-losing-the-attributes](http://stackoverflow.com/questions/10404224/how-to-delete-a-row-from-a-data-frame-without-losing-the-attributes)
- [approaches-to-preserving-objects-attributes-during-extract-replace-operations](http://stackoverflow.com/questions/23841387/approaches-to-preserving-objects-attributes-during-extract-replace-operations)
- [indexing-operation-removes-attributes](http://stackoverflow.com/questions/13432519/indexing-operation-removes-attributes)



## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
